% Cover letter using letter.cls
\documentclass{letter}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

% \addtolength{\topmargin}{-.5in}

%-------------------------
% Personal Information
\newcommand{\CVName}{JOSHUA L. RASMUSSEN}
\newcommand{\CVAddressOne}{12121 Admiralty Way apt. J201}
\newcommand{\CVAddressTwo}{Everett, WA 98204}
\newcommand{\CVPhone}{(425) 760 - 9918}
\newcommand{\CVEmail}{xlr8runner@gmail.com}
\newcommand{\CVWebsite}{http://www.joshrasmussen.com}
\newcommand{\CVGithub}{https://github.com/xlr8runner}
\newcommand{\CVLinkedin}{https://www.linkedin.com/in/josh-rasmussen-95023490}

\begin{document}

\signature{Joshua L. Rasmussen}                  % name for signature
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\begin{letter}{Hiring Manager \\
XYZ Corporation \\
Rt. 56 \\
Anytown, New Jersey 05867}

\begin{center}
{\large\bf \CVName} \\
\CVAddressOne \\ \CVAddressTwo  \\ \CVPhone \\
\CVEmail
\end{center}
\vfill
\opening{Dear Hiring Manager:}

\noindent I was excited to see that you had posted a position as a high school {\bf SUBJECT} teacher at {\bf SCHOOL HERE}.
As you can tell from my resume, I will be a graduate of Seattle Pacific University where I will be completing the requirements for their MTMS (Masters in Teaching Math and Science) program. I will have my completed degree in June 2018 and have already passed the West-B and NES in math to have an endorsement in Secondary level Math.
I also plan on adding a Computer Science endorsement upon certification.

\noindent I am currently at Snohomish High School where I am doing my student teaching and have had the opportunity to be in the classroom for an entire school year. I’ve been helping teach Algebra 1, Pre-Calculus, and an
Algebra Lab class. Mostly I’m excited about the Lab class because we were able to provide extra learning supports to help students who needed them to succeed in their Algebra 1 classes by creating hands-on activities. While completing my student teaching I have taken on the responsibility for after-school tutoring every day. The after-school tutoring is for students who need that extra hour of help on any of their homework which can range from math and science to history and English. I'm incredibly proud of my contribution to Academic Learning Lab and Algebra Lab because through these interventions we have seen a positive effect on those students grades.

\noindent Before this program, I was an engineer for three years in both electrical engineering as well as software engineering and I am excited to for the opportunity to bring these experiences into the classroom. I am confident that this will enrich my daily lessons by being able to provide real-world applications to my students.

\noindent I’m a very driven, well-rounded, and adaptable individual that thrives on coming up with creative ways to solve problems. I am always learning new things, and I believe that makes me a strong asset to your team. I confidently think that I will be able to create a fun and supportive learning environment for students in the classroom. I hope to be considered for an interview to meet you in person. Please feel free to contact me by email or my mobile number to set up a time to talk.

\closing{Sincerely yours,}

% \encl{}					% Enclosures

\end{letter}

\end{document}
